---
title: "Alcohol vs Seat choice"
author: "Melissa Sanchez"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
```{r}
boxplot(alcohol~Seat,data=davisdata)
```  

It appears that those who sit in the back tend to drink more than those who sit in the middle than front. Those in the middle drink more than those who sit in the front. 75% of people who sit in the back drink more than anyone who is sitting in the middle and front.

### get fancy  

```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

It appears that using this data we may be able to reject the null hypothesis. Baising on these box plots, there is a clear difference in how much people drink depending on there seating positions.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The back row is different with there mean being 9.6. The middle row being 3.2. The front row holding the lowest at 1.8.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We will reject this hypothesis, but we will seek clarification on which rows where different from other rows. 

```{r}
plot(TukeyHSD(model1))
```

Using the Tukey plot box we can tell that the front is different from the back, and the middle is different from the back. However there is no difference from the middle and front.

## Conclusions

Because the categorical variable has more than 2 levels, we have to use anova, not a t-test. The Anova showed there is a difference in alchol consumption among the seat locations Tukey HSD show that the differences where in the back row, and not much different compared to the middle and thr front.

